Unsupervised Semantic Mapping for Healthcare Data Storage Schema

### 2021-08-04 ManuScript/IEEEAccess/Revision 1/final/ManuScript.tex

\begin{abstract}
Data, information, and knowledge processing systems, in the domain of healthcare are currently plagued by the heterogeneity at various levels. Current solutions, have focused on developing a standard based, manual intervention mechanism, which requires a large amount of human resource and necessitate realignment of existing systems. State-of-the-art methodologies in the field of natural language processing and machine learning, can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class based classification algorithm. We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer based machine learning models, to create mappings between the data elements. Additionally, the annotated data, collected against five medical schemas and labeled by four annotators is made available for helping future researchers. Our results indicate, that for biased, dependent multi-class text classification, transformer based models provide better results than linguistic and other classical models. In particular, the Robustly Optimized BERT Pretraining Approach (RoBERTa) provides the best schema matching performance by achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human annotated data.
\end{abstract}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.60]{methodology}
	\caption{Methodology for creating schema maps.}
	\label{fig:methodology}
\end{figure*}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.53]{schemas}
	\caption{The five medical schemas used for achieving data interoperability.}
	\label{fig:schema}
\end{figure*}

@@

\begin{figure}[tb!]
	\centering
	\includegraphics[scale=0.65]{suffixAttribute}
	\caption{An example of suffix arrays produced for the attribute ``dateOfAdmission''.}
	\label{fig:suffix_attribute}
\end{figure}

@@

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement}
	\caption{Cohen's Kappa ($\kappa$) score among the four annotators}
	\label{fig:kappaInterAnnotatorAgrement}
\end{figure}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.83]{thresholdSelection}
	\caption{Thresholds selection using MCC scores where t1 indicates the similarity threshold between $class_0$ and $class_{0.5}$, and t2 indicate the similarity threshold between $class_{0.5}$ and $class_1$.}
	\label{fig:thresholdSelection}
\end{figure*}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.83]{evaluation}
	\caption{Performance evaluation of various models using MCC and kappa ($\kappa$) scores.}
	\label{fig:evaluation}
\end{figure*}

\section{Discussion}
\label{discussion}
In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance. The same is also useful for evaluating the performance of unsupervised learning techniques. However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort. While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}. This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge. One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''. According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child. While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}. As a result, the annotations were kept anonymous so as not to induce any bias. Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology. A mode based voting mechanism was then used to resolve the differences between the annotators. The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators. As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy. As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC. The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.

Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the nature of the dataset. Even before annotation, the dataset is bias in favour of unrelated attributes. As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found. In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless. These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy. Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy. These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure. In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric. These graphs are well suited for independent classes as shown by \cite{espindola2005extending}. Additionally, in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$). AUROC and AUPR were thus replaced with our current approach for threshold selection. The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.

\textbf{Transparency}
Through this research we aim to bridge the gap between healthcare schema, which is imperative for providing the medical experts with a complete picture of the patient's health record.

A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al. \cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR). The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations. The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions. However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.

\section{Conclusion}
\label{conclusion}
Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable. However, research and development of ubiquitous health management systems, still require manual interventions by human experts. These approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers. In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques. Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps. Resultantly, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop. We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.

\section*{Acknowledgment}
This research was supported by the MSIT(Ministry of Science and ICT), Korea, under the ITRC(Information Technology Research Center) support program(IITP-2017-0-01629) supervised by the IITP(Institute for Information \& communications Technology Promotion), IITP-2017-0-00655, NRF-2016K1A3A7A03951968, and NRF-2019R1A2C2090504.

\bibliographystyle{unsrt}
\bibliography{references}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_tcc.jpg}}]{Tae-Choong Chung}  received his B.S. degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S. and Ph.D. degrees in Computer Science from KAIST, Republic of Korea, in 1982 and 1987, respectively. Since 1988, he has been with the Department of Computer Science and Engineering, Kyung Hee University, Republic of Korea, where he is now a Professor. His research interests include machine learning, meta search, and robotics.

>>>>

\begin{abstract}
Data, information, and knowledge processing systems, in the domain of healthcare, are currently plagued by heterogeneity at various levels. Current solutions have focused on developing a standard-based, manual intervention mechanism, which requires a large number of human resources and necessitates the realignment of existing systems. State-of-the-art methodologies in the field of natural language processing and machine learning can help to partially automate this process, reducing the resource requirements and providing a relatively good multi-class-based classification algorithm. We present a novel methodology for bridging the gap between various healthcare data management solutions by leveraging the strength of transformer-based machine learning models, to create mappings between the data elements. Additionally, the annotated data, collected against five medical schemas and labeled by four annotators is made available for helping future researchers. Our results indicate, that for biased, dependent multi-class text classification, transformer-based models provide better results than linguistic and other classical models. In particular, the Robustly Optimized BERT Pretraining Approach (RoBERTa) provides the best schema matching performance by achieving a Cohen's kappa score of 0.47 and Matthews Correlation Coefficient (MCC) score of 0.48, with human-annotated data.
\end{abstract}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.60]{methodology_final}
	\caption{Methodology for creating schema maps.}
	\label{fig:methodology}
\end{figure*}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.53]{schemas_final}
	\caption{The five medical schemas used for achieving data interoperability.}
	\label{fig:schema}
\end{figure*}

@@

\begin{figure}[tb!]
	\centering
	\includegraphics[scale=0.65]{suffixAttribute_final}
	\caption{An example of suffix arrays produced for the attribute ``dateOfAdmission''.}
	\label{fig:suffix_attribute}
\end{figure}

@@

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\columnwidth]{kappaInterAnnotatorAgrement_final}
	\caption{Cohen's Kappa ($\kappa$) score among the four annotators}
	\label{fig:kappaInterAnnotatorAgrement}
\end{figure}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.83]{thresholdSelection_final}
	\caption{Thresholds selection using MCC scores where t1 indicates the similarity threshold between $class_0$ and $class_{0.5}$, and t2 indicate the similarity threshold between $class_{0.5}$ and $class_1$.}
	\label{fig:thresholdSelection}
\end{figure*}

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[scale=0.83]{evaluation_final}
	\caption{Performance evaluation of various models using MCC and kappa ($\kappa$) scores.}
	\label{fig:evaluation}
\end{figure*}

\section{Discussion}
\label{discussion}
In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance. The same is also useful for evaluating the performance of unsupervised learning techniques. In the real world, the production and maintenance of these corpora is an expensive task, often requiring extensive human effort and conformance to ethical principles, which can restrict access to critical data for the researchers. While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively assign a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}. Data validity is especially important in the domain of healthcare, where the acquisition, curation, and sharing processes are all encapsulated by the need to ensure correctness as well as privacy and security of the user. Consequently, the availability of healthcare data, its accuracy, and transparency are major concerns for most researchers associated with this domain \cite{Joshi2018}. It is not only important to access the data but also to understand how it was produced, the caveats associated with it, and any assumptions made during or after its acquisition.  
In the case of our annotated dataset, the instances have been labeled by four human experts (two medical practitioners and two computer science graduates), using their subjective knowledge. One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''. According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child. While the selection of this label can be debated from a subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}. As a result, the annotations were kept anonymous so as not to induce any bias. Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology. A mode based voting mechanism was then used to resolve the differences between the annotators. The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators. As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy. As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC. The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextual and relative manner.

Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the dataset's nature. Even before annotation, the dataset is bias in favour of unrelated attributes. As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found. In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless. These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy. Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy. These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure. In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric. These graphs are well suited for independent classes as shown by \cite{espindola2005extending}. Additionally, in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$). AUROC and AUPR were thus replaced with our current approach for threshold selection. The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.

\section{Conclusion}
\label{conclusion}
Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable. However, research and development of ubiquitous health management systems, still require manual interventions by human experts. These approaches require costly resource allocations, which are not possible for small and medium scaled healthcare service providers. In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques. Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps. As a result, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop. We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.

\section*{Acknowledgment}
This research was supported by ITRC(Information Technology Research Center) support program(IITP-2017-0-01629), Grand Information Technology Research Center support program(IITP-2021-2020-0-01489), and IITP-2017-0-00655 supervised by IITP(Institute of Information \& communications Technology Planning \& Evaluation), and National Research Foundation of Korea(NRF) NRF-2019R1A2C2090504 funded by the Korea government(MSIT).

\begin{thebibliography}{10}

	\bibitem{geraci1991ieee}
	Anne Geraci, Freny Katki, Louise McMonegal, Bennett Meyer, John Lane, Paul
	Wilson, Jane Radatz, Mary Yee, Hugh Porteous, and Fredrick Springsteel.
	\newblock {\em IEEE standard computer dictionary: Compilation of IEEE standard
		computer glossaries}.
	\newblock IEEE Press, 1991.

	\bibitem{Himss_url2013}
	{Healthcare Information and Management Systems Society}.
	\newblock {Definition of Interoperability}, 2013.

	\bibitem{khan2013process}
	Wajahat~Ali Khan, Maqbool Hussain, Khalid Latif, Muhammad Afzal, Farooq Ahmad,
	and Sungyoung Lee.
	\newblock Process interoperability in healthcare systems with dynamic semantic
	web services.
	\newblock {\em Computing}, 95(9):837--862, 2013.

	\bibitem{ali2017multi}
	Taqdir Ali, Maqbool Hussain, Wajahat~Ali Khan, Muhammad Afzal, Jamil Hussain,
	Rahman Ali, Waseem Hassan, Arif Jamshed, Byeong~Ho Kang, and Sungyoung Lee.
	\newblock Multi-model-based interactive authoring environment for creating
	shareable medical knowledge.
	\newblock {\em Computer Methods and Programs in Biomedicine}, 150:41--72, 2017.

	\bibitem{snomedct_url}
	{SNOMED Clinical Terminologies}.

	\bibitem{loinc}
	{LOINC}.

	\bibitem{mohammed2010ubiquitous}
	Sabah Mohammed and Jinan Fiaidhi.
	\newblock {\em Ubiquitous Health and Medical Informatics: The Ubiquity 2.0
		Trend and Beyond: The Ubiquity 2.0 Trend and Beyond}.
	\newblock IGI Global, 2010.

	\bibitem{CIMI2015}
	David Johnson.
	\newblock {Clinical Information Modeling Initiative (CIMI)}.
	\newblock Accessed:2021-06-05.

	\bibitem{Satti2020}
	Fahad~Ahmed Satti, Taqdir Ali, Jamil Hussain, Wajahat~Ali Khan, Asad~Masood
	Khattak, and Sungyoung Lee.
	\newblock {Ubiquitous Health Profile (UHPr): a big data curation platform for
		supporting health data interoperability}.
	\newblock {\em Computing}, 2020.

	\bibitem{althubaiti2020combining}
	Sara Althubaiti, {\c{S}}enay Kafkas, Marwa Abdelhakim, and Robert Hoehndorf.
	\newblock Combining lexical and context features for automatic ontology
	extension.
	\newblock {\em Journal of biomedical semantics}, 11(1):1--13, 2020.

	\bibitem{nozaki2019semantic}
	Kenji Nozaki, Teruhisa Hochin, and Hiroki Nomiya.
	\newblock Semantic schema matching for string attribute with word vectors.
	\newblock In {\em 2019 6th International Conference on Computational
		Science/Intelligence and Applied Informatics (CSII)}, pages 25--30. IEEE,
	2019.

	\bibitem{yousfi2020xmatcher}
	Aola Yousfi, Moulay~Hafid El~Yazidi, and Ahmed Zellou.
	\newblock xmatcher: Matching extensible markup language schemas using
	semantic-based techniques.
	\newblock {\em International Journal of Advanced Computer Science and
		Applications}, 11(8):655--665, 2020.

	\bibitem{bulygin2018combining}
	Lev Bulygin.
	\newblock Combining lexical and semantic similarity measures with machine
	learning approach for ontology and schema matching problem.
	\newblock In {\em Proceedings of the XX International Conference “Data
		Analytics and Management in Data Intensive Domains”(DAMDID/RCDL’2018)},
	pages 245--249, 2018.

	\bibitem{martono2017review}
	Galih~Hendro Martono and SN~Azhari.
	\newblock Review implementation of linguistic approach in schema matching.
	\newblock {\em International Journal of Advances in Intelligent Informatics},
	3(1):1--9, 2017.

	\bibitem{alwan2017survey}
	Ali~A Alwan, Azlin Nordin, Mogahed Alzeber, and Abedallah~Zaid Abualkishik.
	\newblock A survey of schema matching research using database schemas and
	instances.
	\newblock {\em International Journal of Advanced Computer Science and
		Applications}, 8(10), 2017.

	\bibitem{kersloot2020natural}
	Martijn~G Kersloot, Florentien~JP van Putten, Ameen Abu-Hanna, Ronald Cornet,
	and Derk~L Arts.
	\newblock Natural language processing algorithms for mapping clinical text
	fragments onto ontology concepts: a systematic review and recommendations for
	future studies.
	\newblock {\em Journal of biomedical semantics}, 11(1):1--21, 2020.

	\bibitem{xu2003discovering}
	Li~Xu and David~W Embley.
	\newblock Discovering direct and indirect matches for schema elements.
	\newblock In {\em Eighth International Conference on Database Systems for
		Advanced Applications, 2003.(DASFAA 2003). Proceedings.}, pages 39--46. IEEE,
	2003.

	\bibitem{zhu2018exploring}
	Xunjie Zhu, Tingfeng Li, and Gerard De~Melo.
	\newblock Exploring semantic properties of sentence embeddings.
	\newblock In {\em Proceedings of the 56th Annual Meeting of the Association for
		Computational Linguistics (Volume 2: Short Papers)}, pages 632--637, 2018.

	\bibitem{kartoun2016methodology}
	Uri Kartoun.
	\newblock A methodology to generate virtual patient repositories.
	\newblock {\em arXiv preprint arXiv:1608.00570}, 2016.

	\bibitem{pan2016design}
	Lijun Pan, Xiaoting Fu, Fangfang Cai, Yu~Meng, and Changjiang Zhang.
	\newblock Design a novel electronic medical record system for regional clinics
	and health centers in china.
	\newblock In {\em 2016 2nd IEEE International Conference on Computer and
		Communications (ICCC)}, pages 38--41. IEEE, 2016.

	\bibitem{inokuchi2007medtakmi}
	Akihiro Inokuchi, Koichi Takeda, Noriko Inaoka, and Fumihiko Wakao.
	\newblock Medtakmi-cdi: interactive knowledge discovery for clinical decision
	intelligence.
	\newblock {\em IBM Systems Journal}, 46(1):115--133, 2007.

	\bibitem{ali2017reconciliation}
	Taqdir Ali and Sungyoung Lee.
	\newblock Reconciliation of snomed ct and domain clinical model for
	interoperable medical knowledge creation.
	\newblock In {\em 2017 39th Annual International Conference of the IEEE
		Engineering in Medicine and Biology Society (EMBC)}, pages 2654--2657. IEEE,
	2017.

	\bibitem{reimers-2019-sentence-bert}
	Nils Reimers and Iryna Gurevych.
	\newblock Sentence-bert: Sentence embeddings using siamese bert-networks.
	\newblock In {\em Proceedings of the 2019 Conference on Empirical Methods in
		Natural Language Processing}. Association for Computational Linguistics, 11
	2019.

	\bibitem{chicco2020advantages}
	Davide Chicco and Giuseppe Jurman.
	\newblock The advantages of the matthews correlation coefficient (mcc) over f1
	score and accuracy in binary classification evaluation.
	\newblock {\em BMC genomics}, 21(1):1--13, 2020.

	\bibitem{gwet2014handbook}
	Kilem~L Gwet.
	\newblock {\em Handbook of inter-rater reliability: The definitive guide to
		measuring the extent of agreement among raters}.
	\newblock Advanced Analytics, LLC, 2014.

	\bibitem{FuzzyWuzzy}
	{Adam Cohen}.
	\newblock Fuzzywuzzy: Fuzzy string matching in python, Jul 8th, 2011.

	\bibitem{mchugh2012interrater}
	Mary~L McHugh.
	\newblock Interrater reliability: the kappa statistic.
	\newblock {\em Biochemia medica}, 22(3):276--282, 2012.

	\bibitem{reidsma2008exploiting}
	Dennis Reidsma and Rieks op~den Akker.
	\newblock Exploiting ‘subjective’annotations.
	\newblock In {\em Coling 2008: Proceedings of the workshop on Human Judgements
		in Computational Linguistics}, pages 8--16, 2008.

	\bibitem{velupillai2010towards}
	Sumithra Velupillai.
	\newblock Towards a better understanding of uncertainties and speculations in
	swedish clinical text--analysis of an initial annotation trial.
	\newblock In {\em Proceedings of the Workshop on Negation and Speculation in
		Natural Language Processing}, pages 14--22, 2010.

	\bibitem{Joshi2018}
	Mohit Joshi and Payal Bhardwaj.
	\newblock {Impact of data transparency: Scientific publications}.
	\newblock {\em Perspectives in Clinical Research}, 9(1):31--36, 2018.

	\bibitem{pavlick2019inherent}
	Ellie Pavlick and Tom Kwiatkowski.
	\newblock Inherent disagreements in human textual inferences.
	\newblock {\em Transactions of the Association for Computational Linguistics},
	7:677--694, 2019.

	\bibitem{espindola2005extending}
	Rog{\'e}rio~P Esp{\'\i}ndola and Nelson~FF Ebecken.
	\newblock On extending f-measure and g-mean metrics to multi-class problems.
	\newblock {\em WIT Transactions on Information and Communication Technologies},
	35, 2005.

	\bibitem{moll2020oncology}
	Jonas Moll and {\AA}sa Cajander.
	\newblock Oncology health-care professionals’ perceived effects of patient
	accessible electronic health records 6 years after launch: a survey study at
	a major university hospital in sweden.
	\newblock {\em Health informatics journal}, 26(2):1392--1403, 2020.

\end{thebibliography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{prof_tcc.jpg}}]{TaeChoong Chung}  received his B.S. degree in Electronic Engineering from Seoul National University, Republic of Korea, in 1980, and his M.S. and Ph.D. degrees in Computer Science from KAIST, Republic of Korea, in 1982 and 1987, respectively. Since 1988, he has been with the Department of Computer Science and Engineering, Kyung Hee University, Republic of Korea, where he is now a Professor. His research interests include machine learning, meta search, and robotics.

### 2021-08-04 ManuScript/IEEEAccess/Revision 1/source/ManuScript.tex

\section{Discussion}
\label{discussion}
In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance. The same is also useful for evaluating the performance of unsupervised learning techniques. However, in the real world the production and maintenance of these corpora is an expensive task, often requiring extensive human effort. While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively provide a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}. This is also evident in the case of our annotated dataset, whereby the instances have been labeled by four human experts (two medical practioners and two computer science graduates), using their subjective knowledge. One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''. According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child. While the selection of this label can be debated from an subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}. As a result, the annotations were kept anonymous so as not to induce any bias. Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology. A mode based voting mechanism was then used to resolve the differences between the annotators. The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators. As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy. As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC. The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextful and relative manner.

Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the nature of the dataset. Even before annotation, the dataset is bias in favour of unrelated attributes. As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found. In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless. These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy. Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy. These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure. In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric. These graphs are well suited for independent classes as shown by \cite{espindola2005extending}. Additionally, in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$). AUROC and AUPR were thus replaced with our current approach for threshold selection. The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.

\textbf{Transparency}
Through this research we aim to bridge the gap between healthcare schema, which is imperative for providing the medical experts with a complete picture of the patient's health record.

A comprehensive survey from 176 experts including physicians and nurses was conducted by Moll et al. \cite{moll2020oncology} to check their perspectives regarding Patient Accessible Electronic Health Record (PAEHR). The authors discovered that the PAEHR positively effect after six years of operations despite negative expectations. The primary concerns revealed was logger meeting time, change in documentation practices, and increasing varies of patients regarding their health conditions. However, attitude of both healthcare service providers and patients are changing positively with respect to PAEHR and its benefits.

\section{Conclusion}
\label{conclusion}
Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable. However, research and development of ubiquitous health management systems, still require manual interventions by human experts. These approaches require costly resource allocations, which is not possible for small and medium scaled healthcare service providers. In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques. Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps. Resultantly, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop. We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.

>>>>

\section{Discussion}
\label{discussion}
In text classification, production and use of a well annotated corpus for supervised and semi-supervised learning is of utmost importance. The same is also useful for evaluating the performance of unsupervised learning techniques. In the real world, the production and maintenance of these corpora is an expensive task, often requiring extensive human effort and conformance to ethical principles, which can restrict access to critical data for the researchers. While there are many factors, influencing this reality, one of the most critical is the perception and cognitive ability of an expert user to subjectively assign a label to an instance \cite{reidsma2008exploiting, velupillai2010towards}. Data validity is especially important in the domain of healthcare, where the acquisition, curation, and sharing processes are all encapsulated by the need to ensure correctness as well as privacy and security of the user. Consequently, the availability of healthcare data, its accuracy, and transparency are major concerns for most researchers associated with this domain \cite{Joshi2018}. It is not only important to access the data but also to understand how it was produced, the caveats associated with it, and any assumptions made during or after its acquisition.  
In the case of our annotated dataset, the instances have been labeled by four human experts (two medical practitioners and two computer science graduates), using their subjective knowledge. One example of this subjective classification, is evident in the raw form of the data instances labeled by ``Annotator3''. According to ``Annotator3'' the relationship between the term ``AdmissionId'' and ``ClinicalHistory'' is parent-child. While the selection of this label can be debated from a subjective view point, changing or removing it or any other label, from the (objective) view point of the computing methodology would be incorrect\cite{pavlick2019inherent}. As a result, the annotations were kept anonymous so as not to induce any bias. Thus, the complete annotated data in its original form became the basis of our threshold selection and model evaluation methodology. A mode based voting mechanism was then used to resolve the differences between the annotators. The consolidated true dataset was then formed based on the agreed upon label by atleast 3 annotators. As pointed out in \cite{reidsma2008exploiting}, the net effect of such a voting mechanism is an increase in the precision of the machine learning classifiers in lieu of, their accuracy. As shown in the results and discussed further on, due to the bias nature of our dataset, accuracy measure is replaced by MCC. The lower scores of agreement between the (annotated data) true labels and predicted labels, have thus been evaluated in a contextual and relative manner.

Throughout this research work, the choice of performance metrics used for threshold selection and model evaluations are also driven by the dataset's nature. Even before annotation, the dataset is bias in favour of unrelated attributes. As established by the human experts and the machine learning model, for 254 attributes involved in 40698 possible pairs only a little over 300 similar instances are found. In these circumstances performance metrics, such as accuracy, precision, and recall are meaningless. These metrics are unable to account for the imbalanced datasets and provide an incorrect view of the classifier's accuracy. Instead metrics such as $F_1$, MCC, and $\kappa$ can provide a true picture of the classifier's accuracy. These metrics are also well suited for evaluating multi-class classifiers, using one vs all or one vs one binarizations of the dataset, as well as consolidating the results into a single measure. In our experimentation, we also evaluated the Area Under the Receiver Operating Characteristic (AUROC) curve and Area Under the Precision Recall (AUPR) curve, as a threshold selection metric. These graphs are well suited for independent classes as shown by \cite{espindola2005extending}. Additionally, in our case it is important to maximize the identification of similar attribute pairs ($class_1$), followed by related ones ($class_{0.5}$) and finally the unrelated ones($class_0$). AUROC and AUPR were thus replaced with our current approach for threshold selection. The benefit of using this kind of dependent classification is its usefulness in practice to identify a small set of similar attribute pairs, which can be used to establish positive results.

\section{Conclusion}
\label{conclusion}
Healthcare information systems are slowly moving towards a standardized approach, whereby the storage, exchange, and usage of health data, information, and knowledge is becoming interoperable. However, research and development of ubiquitous health management systems, still require manual interventions by human experts. These approaches require costly resource allocations, which are not possible for small and medium scaled healthcare service providers. In order to provide data interoperability services to these providers, and automating the process of generating maps between HMIS schema, which can match and transform patient data from a source provider to a target one, it is important to utilize state-of-the-art NLP techniques. Using transformer based pre-trained BERT models, we show the applicability of these techniques on creating the, as yet non-validated, schema maps. As a result, human effort can now focus on validating and verifying the schema maps, which can greatly accelerate the application of healthcare data interoperability, and provide a cohesive ecosystem for ubiquitous healthcare service delivery.
In future, we shall look towards developing a mechanism for schema map storage and evolution, along with expert validation to finally close this loop. We shall also work on re-training some of the existing pre-trained models, to improve the performance of schema map creation.
